Threat detection in online discussions

### 2016-04-01 submission.tex
oppdatert modellnavn

Lastly, we will test the addition of dependency triples to our models. We add
dependency triples consisting of word forms, both alone, and in conjunction
with feature backoffs. As with $n$-gram backoff, we test multiple variations of
backoff, both head-backoff and modifier-backoff. The results reported are the
backoff variant that achieved the best results. As seen in Table
\ref{tab:depbackoff}, the inclusion of word form dependency triples improved
upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for
bag-of-words alone. Dependency triples did not, however, improve upon the
results achieved by our previous best performer with an F-score of $0.6656$. %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
Neither did the addition of backoff improve upon this model. Adding POS backoff
to the `BoW+dep' configuration resulted in a slightly increased F-score of
$0.6298$. However, adding backoff to the `All' feature set only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.

For the development data, our best performer remains the feature set comprising bag-of-word forms, bag-of-lemmas, and word form bigrams and trigrams; with an F-score of $0.6656$. We will refer to this model as `lexical $n$-grams'. % and in the next section we present a brief error analysis before moving on to held-out testing.

@@

\begin{table}
\begin{smaller}
  \begin{center}
    \begin{tabular}{lrrr}
      \toprule      
      & Precision & Recall & F-score\\
      \midrule
      BoW & $0.7325$ & $0.5943$ & $0.6562$ \\
      Combined & $\textbf{0.7532}$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
%      Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\            
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F-score on the held-out test set for the basic BoW model and the best development feature set; the lexical $n$-gram model.}
  \label{tab:heldout}
\end{smaller}
\end{table}

>>>>

Lastly, we will test the addition of dependency triples to our models. We add
dependency triples consisting of word forms, both alone, and in conjunction
with feature backoffs. As with $n$-gram backoff, we test multiple variations of
backoff, both head-backoff and modifier-backoff. The results reported are the
backoff variant that achieved the best results. As seen in Table
\ref{tab:depbackoff}, the inclusion of word form dependency triples improved
upon the simplest model, with an F-score of $0.6240$, compared to $0.6123$ for
bag-of-words alone. Dependency triples did not, however, improve upon the
results achieved by our previous best performer with an F-score of $0.6656$. %, as the best model with dependency triples got an F-score of $0.6586$ compared to our best result of $0.6656$.
Neither did the addition of backoff improve upon this. Adding POS backoff
to the `BoW+dep' configuration resulted in a slightly increased F-score of
$0.6298$. However, adding backoff to the `All' feature set only resulted in poorer F-scores, with the best feature backoff (also POS) resulting in an F-score of $0.6547$.

For the development data then, our best performer remains the feature set comprising bag-of-word forms, bag-of-lemmas, and word form bigrams and trigrams; with an F-score of $0.6656$. We will refer to this model as `lexical $n$-grams'. % fixme: burde kanskje ha introdusert denne termen tidligere?

@@

\begin{table}
\begin{smaller}
  \begin{center}
    \begin{tabular}{lrrr}
      \toprule      
      & Precision & Recall & F-score\\
      \midrule
      BoW & $0.7325$ & $0.5943$ & $0.6562$ \\
      Lexical $n$-grams & $\textbf{0.7532}$ & $\textbf{0.6299}$ & $\textbf{0.6860}$  \\
%      Combined+backoff & $\textbf{0.7703}$ & $0.6085$ & $0.6799$ \\            
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F-score on the held-out test set for the basic BoW model and the best development feature set; the lexical $n$-gram model.}
  \label{tab:heldout}
\end{smaller}
\end{table}
